\RequirePackage[2024-05-01]{latexrelease}

\documentclass[10pt,a4paper,ragged2e,withhyper]{./AltaCV/altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
 
\usepackage{paracol}

\ifxetexorluatex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{LightGrey}{HTML}{000000} 
\definecolor{Blue}{HTML}{1F7F9F}
\definecolor{Purple}{HTML}{3C3744}
\definecolor{Amber}{HTML}{FFBF00}

\colorlet{name}{Blue}
\colorlet{tagline}{Blue}
\colorlet{heading}{Blue}
\colorlet{headingrule}{Amber}
\colorlet{subheading}{Blue}
\colorlet{accent}{Blue}
\colorlet{emphasis}{Blue}
\colorlet{body}{Purple}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}
\name{Alix ANNERAUD}
\tagline{20-year old student in computer science at INSA Rouen Normandie.}

%\photoL{2.8cm}{Photo transparente.png}

\personalinfo{
  \homepage{alix.anneraud.fr}
  \email{alix@anneraud.fr}
  \phone{+33 7 81 85 08 69}
  \github{AlixANNERAUD}
  \linkedin{Alix-ANNERAUD}
  %\location{Rouen, France}\\
}

\makecvheader


\columnratio{0.6}

\begin{paracol}{2}
  \cvsection{\faBriefcase Experience}

  \cvevent{Assistant to the Corporate Relations Department}{INSA Rouen Normandie}{September 2021 -- Ongoing}{}

  Versatile assistance position involving:
  \begin{itemize}
  \item Collecting and optimizing data related to INSA partner companies.
  \item Soliciting partner companies for the collection of apprenticeship tax.
  \item Administrative management of student files.
  \item Conducting alumni surveys for course certification.
  \end{itemize}

  \divider

  \cvevent{Intern on production line}{Renault - Cléon factory}{June 2022 (1 month)}{}

  Assembled rotors and stators for electric motors.

  \smallskip

  \cvsection{\faGraduationCap Education}

  \cvevent{Engineering degree in computer science}{INSA Rouen Normandie}{Sept 2021 -- Ongoing}{Rouen, France}

  \divider

  \cvevent{Scientific baccalaureate (European section) }{Jean-Paul II school}{2021}{Rouen, France}
  Graduated with distinction.

  \divider

  \cvevent{Cambridge B1 Preliminary}{}{2018}{}

  \smallskip

  \cvsection{\faLightbulb Projects}

  \cvevent{Xila}{\url{https://xila.dev}}{}{}
  I am currently working on a personal project – the development of a simple operating system tailored for microcontrollers.
  The primary objective is to establish a standard and user-friendly API, fostering seamless collaboration among diverse software components within a unified ecosystem.
  As part of this endeavor, I am in the process of rewriting a section of the codebase in Rust.

  \divider

  \cvevent{Connected speaker}
  {}
  {}
  {}
  Designed a remote control system for an amplifier card using off-the-shelf components and an ESP32, enhancing home entertainment with versatile audio control.
 
  \medskip

  \switchcolumn

  \cvsection{\faUser About}

  \begin{quote}
    ``I have been studying at INSA Rouen since 2021.
    Currently, I am actively searching for an internship abroad in the IT field to further enhance my practical skills.
    Ideally, the internship would last between 1 and 2 months.
    I'm available between June 17 and August 31, 2024.''
  \end{quote}

  \cvsection{\faThumbsUp Hobbies}

  \cvachievement{\faMicrochip}{I.T. \& electronics}{Passionate about electronics and IT since childhood, I aspire to become an engineer in this field.}

  \divider

  \cvachievement{\faSubway}{Scale modeling}{I have been building a model railway with my father.}

  \divider

  \cvachievement{\faMusic}{Music}{I listen to a lot of music styles and play piano.}

  \cvsection{\faTools Strengths}

  \cvtag{Hard-working}
  \cvtag{Self-taught}
  \cvtag{Persistent}
  \cvtag{Thorough}
  \cvtag{Driver's license}
  \\

  \divider

  \cvtag{C}
  \cvtag{C++}
  \cvtag{Rust}
  \cvtag{Free Pascal}
  \cvtag{Python}
  \cvtag{\LaTeX}
  \cvtag{Linux}
  \cvtag{Embedded systems}

  \cvsection{\faGlobe Languages}

  \textcolor{emphasis}{\textbf{French}} \hfill \textbf{Native}\\

  \divider

  \textcolor{emphasis}{\textbf{English}} \hfill \textbf{Fluent (C1)}\\

  \divider

  \textcolor{emphasis}{\textbf{Spanish}} \hfill \textbf{Basic (A2)}\\

  \divider

  \textcolor{emphasis}{\textbf{German}} \hfill \textbf{Basic (A2)}\\

\end{paracol}

\end{document}