\documentclass[10pt,a4paper,ragged2e,withhyper]{../AltaCV/altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}

\ifxetex
\setmainfont{Roboto Slab}
\setsansfont{Lato}
\renewcommand{\familydefault}{\sfdefault}
\else
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{LightGrey}{HTML}{000000}
\definecolor{Blue}{HTML}{1F7F9F}
\definecolor{Purple}{HTML}{3C3744}
\definecolor{Amber}{HTML}{FFBF00}

\colorlet{name}{Blue}
\colorlet{tagline}{Blue}
\colorlet{heading}{Blue}
\colorlet{headingrule}{Amber}
\colorlet{subheading}{Blue}
\colorlet{accent}{Blue}
\colorlet{emphasis}{Blue}
\colorlet{body}{Purple}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}
\name{Alix ANNERAUD}
\tagline{Engineering student in CS -- 1-year work-study (2/3-day split) from Sep 2026}

%\photoL{2.8cm}{Photo transparente.png}

\personalinfo{
	\printinfo{\faGlobe}{\underline{\url{https://alix.anneraud.fr}}}
	\email{alix@anneraud.fr}
	\phone{+33 7 81 85 08 69}
	\github{AlixANNERAUD}
	\linkedin{Alix-ANNERAUD}
	%\location{Rouen, France}\\
}

\makecvheader

\columnratio{0.6}

\begin{paracol}{2}

	\cvsection{\faBriefcase Experience}

	\cvevent{Network and Telecom Technician}{\href{https://linkt.fr/}{Linkt}}{December 2025 -- Present}{Mont-Saint-Aignan, France}
	Network incident resolution (MPLS VPN, VRRP, FTTH/xDSL/4G) with SLA < 4h. Configuration of Cisco/Keenetic routers, Fortinet firewalls, VoIP (SIP, Centrex). Built a browser extension (WXT/Vue.js) to automate diagnostics and ticket enrichment.

	\divider

	\cvevent{Software engineer intern}{Amazon Spain - \href{https://amazon.jobs/content/en/teams/north-america-stores/upmt}{UPMT}}{May -- August 2025 (4 months)}{Madrid, Spain}
	Full-stack development in Marketing Technology:

	\begin{itemize}
		\item Refactored internal marketing tool with full ownership.
		\item \textbf{Java/Coral/Python}, \textbf{TypeScript/React}, \textbf{AWS} (Lambda, Redshift, CloudFormation, CDK, API Gateway ...).
		\item Large-scale systems across multiple AWS regions.
	\end{itemize}

	\divider

	\cvevent{Research intern}{New York University (NYU)}{June -- August 2024}{New York, USA}
	Gas Source Localization (GSL) project:
	\begin{itemize}
		\item \textbf{Fluid simulations} and \textbf{localization algorithms}.
		\item \textbf{Signal processing} and \textbf{data analysis} in Python.
		\item Design and development of mobile IoT sensors in C++.
	\end{itemize}

	\divider

	\cvevent{Assistant to the Corporate Relations Department}{INSA Rouen Normandie}{September 2021 -- June 2024}{Rouen, France}
	Data collection on partner companies, apprenticeship tax canvassing, and administrative management of student files.

	\cvsection{\faLightbulb Projects}

	\begin{minipage}[t]{0.49\linewidth}
		\cvevent{\normalsize Xila - \underline{\url{https://xila.dev}}}{}{}{}
		{\small \cvtag{Rust}\cvtag{C} - A minimalist and secure operating system for microcontrollers, capable of running WASM applications.}

		\divider

		\cvevent{\normalsize ThéraPIC -- PM - \underline{\href{https://www.becquerel.fr/}{CHB}}}{}{}{}
		{\small \cvtag{Vue.js}\cvtag{Django}\cvtag{PostgreSQL}\cvtag{NLP}\cvtag{Docker} - Led a 6-person agile team (~20h/week) to build a full-stack prescription management app for pharmacists at Centre Henri Becquerel.}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.49\linewidth}
		\cvevent{\normalsize Deez'Nalyzer - \underline{\href{https://github.com/AlixANNERAUD/Deez_Nalyzer}{GitHub}}}{}{}{}
		{\small \cvtag{Vue.js}\cvtag{Django}\cvtag{ML} - A web application for generating playlists and classifying tracks by analyzing MP3 files and listening habits using the Deezer API.}

		\divider

		\cvevent{\normalsize Cartographie - \underline{\href{https://github.com/AlixANNERAUD/Evidential_occupancy_map}{GitHub}}}{}{}{}
		{\small \cvtag{C++}\cvtag{ROS} -  Implementation of an evidential mapping algorithm (EOGM) based on Dempster-Shafer theory, optimized for real-time performance.}
	\end{minipage}

	\medskip

	\switchcolumn

	\cvsection{\faUser About}

	\begin{quote}
		``Software engineer with 2 international internships, expertise in low-level systems, AWS cloud, and full-stack development. \textbf{1\textsuperscript{st} place} Jeanne d'Hack CTF 2026 \& Cod'INSA 2025. Seeking a \textbf{work-study contract} (September 2026).''
	\end{quote}

	\cvsection{\faGraduationCap Education}

	\cvevent{Dipl\^{o}me d'Ing\'enieur in Computer Science}{INSA Rouen Normandie}{2021 - 2027}{Rouen, France}
	4th year completed (eq.~M1) -- resuming September 2026, open to \textbf{work-study}.

	\divider

	\cvevent{Scientific baccalaureate (European section) }{Jean-Paul II school}{2021}{Rouen, France}
	Graduated with distinction.

	\cvsection{\faGlobe Languages}

	\textcolor{emphasis}{\textbf{French}} \hfill \textbf{Native}\\

	\divider

	\textcolor{emphasis}{\textbf{English}} \hfill \textbf{Fluent (TOEIC : 975 - C1)}\\

	\divider

	\textcolor{emphasis}{\textbf{Spanish}} \hfill \textbf{Basic (A2)}\\

	\divider

	\textcolor{emphasis}{\textbf{German}} \hfill \textbf{Basic (A2)}\\

	\cvsection{\faTools Strengths}

	\cvtag{Problem-solving}
	\cvtag{Autonomous}
	\cvtag{Teamwork}
	\cvtag{Adaptable}
	\cvtag{Driver's license}
	\\

	\divider

	\cvtag{Rust}
	\cvtag{C/C++}
	\cvtag{Python}
	\cvtag{Java}
	\cvtag{TypeScript}
	\cvtag{Vue.js}
	\cvtag{React}
	\cvtag{Django}
	\cvtag{AWS}
	\cvtag{Docker}
	\cvtag{CI/CD}
	\cvtag{Linux}
	\cvtag{MongoDB}
	\cvtag{Hadoop}
	\cvtag{Embedded systems}
	\cvtag{Deep learning}
	\cvtag{Image processing}
	\cvtag{\LaTeX}

\end{paracol}

\end{document}
